saycam full dataset analysis

### 2020-01-14 analysis/analysis_fulldataset.Rmd
add code for cropped analysis

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)

@@

### Load in detections from preprocessed Rdata file; 
```{r eval=FALSE}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/openpose_detections.RData')
```

### Preprocess data (doesn't exceute; loads processed data below)
```{r eval=FALSE}
# get shortened video names so they match across all files
all_video_names = as.tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and flip the videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

@@

@@

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

@@

## save this data so this doesn't have to be redone again
save(d_all, file = '../data/openpose_detections_filtered.RData')

@@

>>>>

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)
```

@@

### Load in detections & bounding boxes from preprocessed Rdata file; 
```{r eval=FALSE}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/openpose_detections.RData')

### Preprocess data (doesn't execute in markdown; loads processed data below)
```{r eval=FALSE}
# get shortened video names so they match across all files
all_video_names = as.tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array for detections & bb (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and exclude bad videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name) 
remove(detections)
```

### Now do the same for bounding box data
```{r}
load('../data/vid_info.RData')
load("../data/all_bounding_boxes.Rdata")

bb_all <- df
bb_all$vid_name = as.factor(bb_all$vid_name)
levels(bb_all$vid_name) <- all_video_names$vid_name

bb_all <- bb_all %>%
  filter(!vid_name %in% flipped_videos$vid_name) 
  left_join(vid_info, by='vid_name') 
  #

```{r}
# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

@@

bb_all <- bb_all %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

@@

## save this data so this doesn't have to be redone again
save(d_all, file = '../data/openpose_detections_filtered.RData')
```

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
```{r}
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

@@

@@

## Cropped analysis
```{r}
## Import bounding boxes data
height_px = 480; width_px = 640

# make etra DVs & age variable
bb_all = bb_all %>%
  mutate(height_y = height*height_px, width_x = width*width_px, area = (height_y*width_x)/(height_px*width_px)) %>%
  mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2)  %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(x/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

detections_cropped <- bb_all %>%
  filter(height <.6) %>%  ## cut off bottom part of frame
  filter(mean_conf > 0) %>% ## look at detections
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(hand_detected = (length(label=="hand")>0), face_detected = (length(label=="face")>0)) %>%
  distinct(vid_name, frame, age_days, child_id, face_detected, hand_detected)
```

### Now plot faces-hands for the cropped analysis
```{r}
summary_by_age_cropped <- detections_cropped %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_detected), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)

ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands (CROPPED)') + 
  xlab('Age (months)')
